\documentclass[12pt]{article}

\usepackage{fullpage}

\author{Eric Dilmore, Andrew Julian, Corrin Thompson, and Ian Brown}
\title{Final Project Proposal: The Game of Life}
\date{September 10, 2014}

\begin{document}
  \maketitle

  \section{Abstract}

  Our group will be making Conway's Game of Life in the MIPS assembly language.
  The program will read from the starting condition from a file submitted by the
  user. The state will then step one frame at a time, with each cell obeying
  all of the rules of the Game of Life. If we have time, we will attempt to
  allow for variable time deltas.

  \section{Motivation}

  We understand the project in higher level languages, but we wanted to explore
  its implementation in an exceptionally low language. Also, we like watching
  pretty patterns on the screen.

  \section{Task Delegation}

  At this point in time, it is hard to know what kinds of tasks will be
  necessary. However, we believe that the four major tasks will be array
  management, program logic, file input/output, and output to screen.

  Tenatively, Ian will work on array management, Eric will work on program
  logic, Corrin will work on file IO, Andrew will work on screen output.

  \section{Timeline}

  Within a week of learning subroutine commands (approximately October 15), we
  will come up with standard interfaces for file IO, screen IO, and array
  manipulation. These will be used as placeholders for actual subroutines, which
  will be written by each team member over the course of the semester.

  However, due to the fact that we need a deliverable on October 6, we will also
  begin figuring out each part on its own prior to that. We will have pseudocode
  written by October 1 for each part, and we will have discussed the pseudocode
  as a group.

\end{document}
